Models

### 2021-09-22 analysis/05_model_metrics.Rmd
Add formula to model table output

  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit$result), model_id = model_id, warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
}

>>>>

  tidy(fit$result) %>%
   mutate(metric = metric_name, model = list(fit$result), 
          model_id = model_id, formula = formula, 
          warning = ifelse(length(fit$warnings) == 0, NA, fit$warnings))
}
